---
title: "Reproduction Code for Supplementary Tables S1-S10"
author: "Analysis for 'Symbolic Incentives in High-Stakes Prosocial Behavior'"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    toc: yes
    fig_caption: yes
---

```{r setup, include=FALSE}
# Global settings for code chunks
knitr::opts_chunk$set(
  echo = TRUE,       # Show code so reviewers can follow
  message = FALSE,
  warning = FALSE,
  fig.align = 'center'
)

# Load necessary libraries
library(tidyverse)
library(knitr)      # For creating tables
library(lmtest)
library(sandwich)
library(margins)
library(modelsummary)
```

# Introduction

This document provides the R code to reproduce Supplementary Tables S1 through S10. The code reads from `reproducible_dataset.csv`, a cleaned dataset containing only the variables necessary for this analysis.

```{r load-data}
# Load the clean, reproducible dataset
df <- read_csv('reproducible_dataset.csv')

# Define the two main analysis samples for convenience
baseline_sample <- df
study_sample <- df %>% filter(is_study_sample == TRUE)
```

\newpage

# Table S1: Study Sample Representativeness

This table compares the characteristics of the study sample to the general US population.

```{r table-s1}
# Create a summary of the study sample
s1_study_summary <- study_sample %>%
  summarise(
    `Female` = mean(is_female, na.rm = TRUE),
    `White` = mean(race == "White", na.rm = TRUE),
    `Hispanic` = mean(race == "Hispanic", na.rm = TRUE),
    `Other Race` = mean(race == "Other", na.rm = TRUE),
    `Black` = mean(race == "Black", na.rm = TRUE),
    `Asian` = mean(race == "Asian", na.rm = TRUE),
    `Age (years)` = mean(age, na.rm = TRUE),
    `Prior Plasma Donation` = mean(prior_plasma_donation, na.rm = TRUE),
    `AB+ or AB- Blood Type` = mean(is_ab_blood_type, na.rm = TRUE),
    `Annual Donation Avg.` = mean(avg_annual_donations, na.rm = TRUE),
    `Median Income ($)` = mean(zip_median_income, na.rm = TRUE),
    `Midwest Region` = mean(us_region == "Midwest", na.rm = TRUE),
    `Northeast Region` = mean(us_region == "Northeast", na.rm = TRUE),
    `South Region` = mean(us_region == "South", na.rm = TRUE),
    `West Region` = mean(us_region == "West", na.rm = TRUE),
    `Urban Region` = mean(is_urban, na.rm = TRUE),
    `COVID-19 Incidence` = mean(county_covid_per_100k, na.rm = TRUE)
  ) %>%
  pivot_longer(everything(), names_to = "Characteristic", values_to = "Study Sample")

# Manually create the US Population data frame
us_pop_data <- tribble(
  ~Characteristic,             ~`US Population`,
  "Female",                    0.508, "White",                     0.763,
  "Hispanic",                  0.185, "Other Race",                0.03,
  "Black",                     0.134, "Asian",                     0.06,
  "Age (years)",               38.10, "Prior Plasma Donation",     NA,
  "AB+ or AB- Blood Type",     0.040, "Annual Donation Avg.",      NA,
  "Median Income ($)",         67521.00, "Midwest Region",            0.21,
  "Northeast Region",          0.17, "South Region",              0.38,
  "West Region",               0.24, "Urban Region",              0.807,
  "COVID-19 Incidence",        4224
)

# Join the two summaries and display the table using kable
table_s1 <- left_join(s1_study_summary, us_pop_data, by = "Characteristic")
kable(table_s1, caption = "Table S1: Study Sample Representativeness", digits = 3, format = "latex", booktabs = TRUE)
```

\newpage

# Table S2: Balance Check

This table checks for balance on covariates between the treatment and control groups.

```{r table-s2}
# Panel A: Study Sample Balance
panel_a <- study_sample %>%
  group_by(treatment_group) %>%
  summarise(
    Female = mean(is_female), White = mean(race == "White"), Age = mean(age),
    `Prior Plasma Donation` = mean(prior_plasma_donation),
    `Annual Donation Avg.` = mean(avg_annual_donations),
    `Median Income` = mean(zip_median_income), `Urban Region` = mean(is_urban),
    `COVID-19 Incidence` = mean(county_covid_per_100k)
  ) %>%
  pivot_longer(-treatment_group, names_to = "Characteristic") %>%
  pivot_wider(names_from = treatment_group, values_from = value)

kable(panel_a, caption = "Table S2 (Panel A): Study Sample Demographics Balance", digits = 2, format = "latex", booktabs = TRUE)

# Panel B: Baseline Sample Selection Criteria Balance
panel_b <- baseline_sample %>%
  group_by(treatment_group) %>%
  summarise(`Opened Email` = mean(email_opened), `No Phone Contact` = mean(no_phone_contact)) %>%
  pivot_longer(-treatment_group, names_to = "Characteristic") %>%
  pivot_wider(names_from = treatment_group, values_from = value)

kable(panel_b, caption = "Table S2 (Panel B): Sample Selection Criteria Balance", digits = 2, format = "latex", booktabs = TRUE)
```

\newpage

# Table S3: Attrition Information

This table shows the number of donors enrolled, analyzed, and excluded.

```{r table-s3}
table_s3 <- baseline_sample %>%
  mutate(ExclusionReason = case_when(
    is_study_sample == FALSE & email_opened == 0 & no_phone_contact == 0 ~ "Excluded (Both)",
    is_study_sample == FALSE & email_opened == 0 ~ "Excluded (Did Not Open)",
    is_study_sample == FALSE & no_phone_contact == 0 ~ "Excluded (Phone Contact)",
    TRUE ~ "Analyzed (Study Sample)"
  )) %>%
  group_by(treatment_group) %>%
  count(ExclusionReason) %>%
  pivot_wider(names_from = ExclusionReason, values_from = n)

kable(table_s3, caption = "Table S3: Attrition Information", format = "latex", booktabs = TRUE)
```

\newpage

# Table S4: Main Analysis (Average Marginal Effects)

This table shows the Average Marginal Effects (AMEs) from logistic regressions on the primary outcomes.

```{r table-s4}
# Define the control variables for the models
controls <- "is_female + age + race + prior_plasma_donation + bloodtype_group + avg_annual_donations + zip_median_income + us_region + is_urban + county_covid_per_100k"

# Run models
m1 <- glm(as.formula(paste("appointment_within_48h ~ treatment_group + factor(wave)")), data = study_sample, family = "binomial")
m2 <- glm(as.formula(paste("appointment_within_48h ~ treatment_group + factor(wave) +", controls)), data = study_sample, family = "binomial")
m3 <- glm(as.formula(paste("donated_within_13d ~ treatment_group + factor(wave)")), data = study_sample, family = "binomial")
m4 <- glm(as.formula(paste("donated_within_13d ~ treatment_group + factor(wave) +", controls)), data = study_sample, family = "binomial")

# Helper function to extract and format AMEs correctly
get_ame <- function(model) {
  s <- summary(margins(model))
  # Find the treatment effect row
  treatment_row <- s %>% filter(grepl("treatment_group", factor))
  
  # Format the estimate with stars and the standard error
  stars <- case_when(treatment_row$p < 0.01 ~ "*", treatment_row$p < 0.05 ~ "*", treatment_row$p < 0.1 ~ "+", TRUE ~ "")
  estimate_str <- paste0(sprintf("%.4f", treatment_row$AME), stars)
  se_str <- paste0("(", sprintf("%.4f", treatment_row$SE), ")")
  
  return(c(estimate_str, se_str))
}

# Manually build the results table to ensure correctness
results_table <- data.frame(
  Term = c("Symbolic Incentives", ""),
  `(1) Appt. Creation` = get_ame(m1),
  `(2) Appt. Creation` = get_ame(m2),
  `(3) Donation` = get_ame(m3),
  `(4) Donation` = get_ame(m4)
)

# Add GOF stats
gof_rows <- data.frame(
  Term = c("Num.Obs.", "Wave FE", "Controls"),
  `(1) Appt. Creation` = c(nobs(m1), "Yes", "No"),
  `(2) Appt. Creation` = c(nobs(m2), "Yes", "Yes"),
  `(3) Donation` = c(nobs(m3), "Yes", "No"),
  `(4) Donation` = c(nobs(m4), "Yes", "Yes")
)

# Combine and print using kable
final_table_s4 <- bind_rows(results_table, gof_rows)
kable(final_table_s4, caption = "Table S4: Effect of Symbolic Incentives (AMEs from Logistic Regression)", booktabs = TRUE, format = "latex", align = 'lcccc')
```

\newpage

# Table S5: Intent-to-Treat (ITT) Analysis

This table repeats the main analysis on the full baseline population.

```{r table-s5}
# Run models on the baseline sample
m1_itt <- glm(as.formula(paste("appointment_within_48h ~ treatment_group + factor(wave)")), data = baseline_sample, family = "binomial")
m2_itt <- glm(as.formula(paste("appointment_within_48h ~ treatment_group + factor(wave) +", controls)), data = baseline_sample, family = "binomial")
m3_itt <- glm(as.formula(paste("donated_within_13d ~ treatment_group + factor(wave)")), data = baseline_sample, family = "binomial")
m4_itt <- glm(as.formula(paste("donated_within_13d ~ treatment_group + factor(wave) +", controls)), data = baseline_sample, family = "binomial")

# Manually build the results table
results_table_itt <- data.frame(
  Term = c("Symbolic Incentives", ""),
  `(1) Appt. Creation` = get_ame(m1_itt),
  `(2) Appt. Creation` = get_ame(m2_itt),
  `(3) Donation` = get_ame(m3_itt),
  `(4) Donation` = get_ame(m4_itt)
)

gof_rows_itt <- data.frame(
  Term = c("Num.Obs.", "Wave FE", "Controls"),
  `(1) Appt. Creation` = c(nobs(m1_itt), "Yes", "No"),
  `(2) Appt. Creation` = c(nobs(m2_itt), "Yes", "Yes"),
  `(3) Donation` = c(nobs(m3_itt), "Yes", "No"),
  `(4) Donation` = c(nobs(m4_itt), "Yes", "Yes")
)

final_table_s5 <- bind_rows(results_table_itt, gof_rows_itt)
kable(final_table_s5, caption = "Table S5: ITT Analysis on Baseline Population (AMEs)", booktabs = TRUE, format = "latex", align = 'lcccc')
```

\newpage

# Table S6: OLS Regressions

This table shows the main results using OLS with robust standard errors.

```{r table-s6}
# Run OLS models
m1_ols <- lm(as.formula(paste("appointment_within_48h ~ treatment_group + factor(wave)")), data = study_sample)
m2_ols <- lm(as.formula(paste("appointment_within_48h ~ treatment_group + factor(wave) +", controls)), data = study_sample)
m3_ols <- lm(as.formula(paste("donated_within_13d ~ treatment_group + factor(wave)")), data = study_sample)
m4_ols <- lm(as.formula(paste("donated_within_13d ~ treatment_group + factor(wave) +", controls)), data = study_sample)

models_ols <- list(
  "(1) Appt. Creation" = m1_ols, "(2) Appt. Creation" = m2_ols,
  "(3) Donation" = m3_ols, "(4) Donation" = m4_ols
)

modelsummary(models_ols,
             title = "Table S6: Effect of Symbolic Incentives (OLS with Robust SEs)",
             fmt = 4, estimate = "{estimate}{stars}", statistic = "({std.error})",
             vcov = "HC1",
             coef_map = c("treatment_groupSymbolic Incentives" = "Symbolic Incentives"),
             gof_map = c("nobs"),
             add_rows = data.frame(
               "term" = c("Wave FE", "Controls"),
               "(1) Appt. Creation" = c("Yes", "No"), "(2) Appt. Creation" = c("Yes", "Yes"),
               "(3) Donation" = c("Yes", "No"), "(4) Donation" = c("Yes", "Yes")
             ),
             output = "latex")
```

\newpage

# Table S7: Different Time Windows

This table shows logistic regression coefficients for outcomes measured over different time horizons.

```{r table-s7}
# Run models with different DVs
m1_tf <- glm(as.formula(paste("appointment_within_24h ~ treatment_group + factor(wave) +", controls)), data = study_sample, family = "binomial")
m2_tf <- glm(as.formula(paste("appointment_within_7d ~ treatment_group + factor(wave) +", controls)), data = study_sample, family = "binomial")
m3_tf <- glm(as.formula(paste("appointment_anytime ~ treatment_group + factor(wave) +", controls)), data = study_sample, family = "binomial")
m4_tf <- glm(as.formula(paste("donated_anytime ~ treatment_group + factor(wave) +", controls)), data = study_sample, family = "binomial")

models_tf <- list(
  "(1) Appt. (24h)" = m1_tf, "(2) Appt. (7d)" = m2_tf,
  "(3) Appt. (Anytime)" = m3_tf, "(4) Donation (Anytime)" = m4_tf
)

modelsummary(models_tf,
             title = "Table S7: Effect of Symbolic Incentives over Different Time Windows (Logit Coefficients)",
             fmt = 4, estimate = "{estimate}{stars}", statistic = "({std.error})",
             coef_map = c("treatment_groupSymbolic Incentives" = "Symbolic Incentives"),
             gof_map = c("nobs"),
             add_rows = data.frame(
               "term" = c("Wave FE", "Controls"),
               "(1) Appt. (24h)" = c("Yes", "Yes"), "(2) Appt. (7d)" = c("Yes", "Yes"),
               "(3) Appt. (Anytime)" = c("Yes", "Yes"), "(4) Donation (Anytime)" = c("Yes", "Yes")
             ),
             output = "latex")
```

\newpage

# Table S8: Unsubscription and Total Donations

This table shows OLS results for secondary outcomes.

```{r table-s8}
# Run models for secondary outcomes
m1_sec <- lm(as.formula(paste("unsubscribe ~ treatment_group + factor(wave)")), data = study_sample)
m2_sec <- lm(as.formula(paste("unsubscribe ~ treatment_group + factor(wave) +", controls)), data = study_sample)
m3_sec <- lm(as.formula(paste("total_donations_post_treatment ~ treatment_group + factor(wave)")), data = study_sample)
m4_sec <- lm(as.formula(paste("total_donations_post_treatment ~ treatment_group + factor(wave) +", controls)), data = study_sample)

models_sec <- list(
  "(1) Unsubscribe" = m1_sec, "(2) Unsubscribe" = m2_sec,
  "(3) Total Donations" = m3_sec, "(4) Total Donations" = m4_sec
)

modelsummary(models_sec,
             title = "Table S8: Effect on Unsubscription and Total Donations (OLS with Robust SEs)",
             fmt = 4, estimate = "{estimate}{stars}", statistic = "({std.error})",
             vcov = "HC1",
             coef_map = c("treatment_groupSymbolic Incentives" = "Symbolic Incentives"),
             gof_map = c("nobs"),
             add_rows = data.frame(
               "term" = c("Wave FE", "Controls"),
               "(1) Unsubscribe" = c("Yes", "No"), "(2) Unsubscribe" = c("Yes", "Yes"),
               "(3) Total Donations" = c("Yes", "No"), "(4) Total Donations" = c("Yes", "Yes")
             ),
             output = "latex")
```

\newpage

# Table S9: Heterogeneous Treatment Effects

This table explores whether the treatment effect varies across pre-registered subgroups.

```{r table-s9}
# Define models with interaction terms
hte_models <- list(
  "Female" = lm(appointment_within_48h ~ treatment_group * is_female + factor(wave), data = study_sample),
  "High Prior Donations" = lm(appointment_within_48h ~ treatment_group * high_prior_donations + factor(wave), data = study_sample),
  "Urban" = lm(appointment_within_48h ~ treatment_group * is_urban + factor(wave), data = study_sample),
  "Majority Dem. County" = lm(appointment_within_48h ~ treatment_group * is_majority_dem_county + factor(wave), data = study_sample)
)

modelsummary(hte_models,
             title = "Table S9: Heterogeneous Treatment Effects on Appointment Creation",
             fmt = 3, estimate = "{estimate}{stars}", statistic = "({std.error})",
             vcov = "HC1",
             coef_rename = c(
               "treatment_groupSymbolic Incentives" = "Treatment Effect (Symbolic Incentives)",
               "is_femaleTRUE" = "Baseline (Female)",
               "high_prior_donationsTRUE" = "Baseline (High Donor)",
               "is_urbanTRUE" = "Baseline (Urban)",
               "is_majority_dem_countyTRUE" = "Baseline (Dem. County)",
               "treatment_groupSymbolic Incentives:is_femaleTRUE" = "Interaction: Trt x Female",
               "treatment_groupSymbolic Incentives:high_prior_donationsTRUE" = "Interaction: Trt x High Donor",
               "treatment_groupSymbolic Incentives:is_urbanTRUE" = "Interaction: Trt x Urban",
               "treatment_groupSymbolic Incentives:is_majority_dem_countyTRUE" = "Interaction: Trt x Dem. County"
             ),
             gof_map = "nobs", output = "latex")
```

\newpage

# Table S10: Intention-Behavior Gap

This table analyzes the effect of the treatment on the gap between scheduling an appointment and actually donating.

```{r table-s10}
# Filter for the relevant population: those who made an appointment
gap_sample <- study_sample %>% filter(!is.na(intention_behavior_gap))

# Run models
m1_gap <- glm(intention_behavior_gap ~ treatment_group + factor(wave), data = gap_sample, family = "binomial")
m2_gap <- glm(intention_behavior_gap ~ treatment_group + factor(wave) + is_female + age + race, data = gap_sample, family = "binomial")

models_gap <- list(
  "(1) No Controls" = m1_gap,
  "(2) With Controls" = m2_gap
)

modelsummary(models_gap,
             title = "Table S10: Effect on Intention-Behavior Gap (Logit Coefficients)",
             fmt = 3, estimate = "{estimate}{stars}", statistic = "({std.error})",
             coef_map = c("treatment_groupSymbolic Incentives" = "Symbolic Incentives"),
             gof_map = c("nobs"),
             add_rows = data.frame(
               "term" = c("Wave FE", "Controls"),
               "(1) No Controls" = c("Yes", "No"),
               "(2) With Controls" = c("Yes", "Yes")
             ),
             output = "latex")
```